---
title: "Network generator"
author: "Philippe Mongeon"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

```

# Objectives

The goal is to generate a co-author network from the Bibliobox template.

## Load packages

Here I load the tidyverse package for the reading and wrangling of data and readxl to read the file from bibliobox

```{r}
library(tidyverse)
library(readxl)
```

## Load the data

We load the CSV generated from bibliobox app

```{r eval=FALSE}

openalex_data <- read_xlsx("data/BiblioBox_1.xlsx")
```

### Extract authors data

First we want to create a tibble called authorships and store in it the custom_id and the

```{r}
auhtorships <- openalex_data %>% 
  select(custom_id, authors) %>% 
  separate_rows(authors, sep=", ")
```

```{r}
network <- authorships %>% 
  inner_join(authorships, by="custom_id") %>% 
  filter(authors.x < authors.y) %>%
  group_by(authors.x, authors.y) %>%
  summarize(weight = n()) %>% 
  mutate(type = "undirected") %>% 
  rename(source = authors.x, target = authors.y)
```
